%%____________________________________________________________________________||
\section{Introduction}
\label{sec:intro}

In this note we summarise the search for WIMPs using an extension of the RA1 analysis.
Because the exact mechanism in which DM couples to the Standard Model is unknown a very large range of possible collider kinematics 
and signatures need to be probed. Therefore we consider a special kinematic variables,  $\alpha_{\textrm T}$, to maximise
 the sensitivity and use all available topologies, for example mono-jet, multi-jet and heavy quarks, in one analysis.  
The \alphat variable allows to to efficiently select candidate signal events with genuine missing transverse momentum while
providing robust rejection against QCD multijet background events. In a similar approach CMS has been searching for
 supersymmetry (SUSY) in proton-proton collisions data collected during LHC Run~1. With data at a centre-of-mass energy of 7 TeV collected in
2010 and 2011, the \alphat analysis has excluded a large parameter space of the constrained minimal supersymmetric extension of the
standard model (CMSSM) \cite{Khachatryan:2011tk, Chatrchyan:2011zy, Chatrchyan:2012wa} and a parameter space of simplified models
\cite{Chatrchyan:2012wa}. With data at a centre-of-mass energy of 8 TeV collected and promptly reconstructed in 2012, the \alphat analysis
further excluded a parameter space of simplified models \cite{Chatrchyan:2013lya}. Additional sets of data which were
collected in 2012 but were reconstructed later during the LHC Long Shutdown 1 (LS1) are called the ``parked data'', which contain data
for events triggered with lower energy thresholds~\cite{CMS_AN_2013-366}.
%The review of the \alphat analysis of the parked data \cite{CMS_AN_2013-366} is ongoing.  
The search strategy in this note is an extension of that in Ref. \cite{CMS_AN_2013-366}.

With the start of Run 2 in June 2015 the LHC delivers proton-proton collisions at a higher centre-of-mass
energy of 13 TeV. The higher energy collision considerably increases the production cross sections of possible dark matter production.
The \alphat analysis is particularly suited for this search and has potential for
discovery in early data. The reconstruction of missing transverse momentum in different collider 
environment or at new collider energy is typically very challenging and often requires an extended period of
development. However, the \alphat variable is designed to provide robust discriminating power between sources of genuine and ``fake''
(\eg instrumental) \met, as well as using an estimator of \met that
relies solely on the vector sum of jet transverse momenta (\mht).
%can effectively select events with missing transverse momentum without
%directly using the reconstructed missing transverse momentum.

%The nature of dark matter (DM) is one of the outstanding problems in
%particle physics and a massive weakly interactive particle (WIMP) is highly motivated. 
%A WIMP is not a specific elementary particle, but rather a broad class of possible particles.
%The most highly scrutinized thermal relic DM candidate is the lightest
%neutralino particle of supersymmetric (SUSY) theories. The
%neutralino is particularly well-motivated since, in addition to solving the DM problem, SUSY extensions of the SM contain a number 
%of other attractive features both for particle physics and in early
%Universe cosmology. Most prominently known, is that 
%SUSY does not only provide an excellent DM candidate but also solves the fine-tuning problem.
%However, not only SUSY but also non-supersymmetric models of physics beyond the standard model predict the production of DM at 
%LHC Run~2. 

%The \alphat variable
%efficiently selects events that potentially contain DM candidates
%produced in the collisions. In Run~2, we extend the \alphat analysis
%to significantly improve the acceptance to dark matter production at
%the LHC.

%The study in this note started as part of the PHYS14 exercise
%\cite{PHYS14} which focused on preparation of the Run~2 physics analyses. 
%In this note, weuse MC event samples generated for this exercise. 
%Events in these samples are simulated under conditions anticipated in early LHC Run~2,
%e.g, the centre-of-mass energy, the bunch-spacing, the number of the
%interactions per bunch crossing.

%Section \ref{sec:strategy} discusses changes in the search methods
%made since Run~1. Sec.~\ref{sec:alphatdef} defines the \alphat
%variable.  Section \ref{sec:datasets} lists the data sets used in this
%note.  Section \ref{sec:triggers} describes the preparation of the
%triggers for Run~2. Section \ref{sec:objects} defines the physics
%objects used in this note. Section \ref{sec:selection} describes how
%events are selected. Section \ref{sec:yields} shows the expected event
%yields in the signal and control regions. While Section \ref{sec:qcd}
%discusses how multijet background events are controlled, Section
%\ref{sec:backgroundmet} estimates background from other
%processes. Then, Sec.~\ref{sec:systematics} discusses systematic
%uncertainties in the estimates. With likelihood models introduced in
%Section \ref{sec:likelihood}, we interpret the results in simplified
%SUSY models in Sec.~\ref{sec:susy} and Dark Matter models in
%\ref{sec:darkmatter}. Finally Sec.~\ref{sec:summary} summarises this
%exercise.

%%____________________________________________________________________________||
