\section{Summary}
\label{sec:summary}

We report on the prospects for a missing energy plus jet search that
is sensitive to a wide range of potential dark matter models.
The analysis follows an inclusive approach designed to capture a wide
scope of possible final states, use of robust methods to be
insensitive to multijet production, instrumental effects and MC
mis-modelling. Thus making it ideal for early data discoveries.
The original $\alpha_\textrm{T}$ analysis has been considerably extended  been improved in several areas, 
including an increase in the acceptance of the signal region and an optimisation of
the signal event categorisation. By relaxing the minimal jet multiplicity 
to as well include single jet events and adding an orthogonal jet selection with a lower 
\Pt requirement on the second leading jet. This leads to 
significantly improved acceptance to compressed SUSY and Dark Matter
models.

Candidate signal events are binned according to the number of
reconstructed jets, the number of jets identified to originate from
bottom quarks, and the scalar and vector sums of the transverse energy
of jets. The sum of standard model backgrounds per bin is estimated
from a simultaneous binned likelihood fit to event yields in the
signal region and \mj, \mmj, and \gj control samples. The
analysis relies heavily on methods and cross-checks derived from the
data control samples to demonstrate control of the SM background
predictions. 


Preliminary projections are presented for DM
simplified models using currently recorded $\sqrt{s} =$ 13~TeV data and $2.1$\ifb of data.
