%%____________________________________________________________________________||
\section{Data sets}
\label{sec:datasets}

In this note, we use proton-proton collision data at $\sqrt{s} =$ 13~TeV
being collected in 2015. Table~\ref{tab:datasets_data} lists the names of
the data sets relevant for the analysis. The integrated luminosities
shown in the table are the sizes of the certified data for each data set
at the time of writing. Since the data collection for the year 2015 and
the certification of the data are ongoing, the sizes of the data sets
that will be used in the final version of the note will be different
from the sizes that the table indicates.

This version of the note uses subsets of the data listed in the table.
As the analysis is actively ongoing, different sections of this note
might use different sizes of the data. The data sizes used in particular
studies in the note might be indicated in relevant sections, tables or
figures.

We are performing the blind analysis. In this version of the note, the
data in the signral region is blinded. In the signral region, only the
149.48 of the certified data agreed upton to unblind in the SUS PAG are
analysed. No data in the control regions is blinded.

Table~\ref{tab:datasets_bkg} lists the data sets of simulated events
of the standard model background processes used in this note. In these
data sets, in addition to the main interaction, each event contains on
average 20 minimum bias interactions which simulate multiple
interactions per bunch-crossing (in-time pileup). The expected detector
signal from previous or following bunch crossings (out-of-time pileup)
with 25ns bunch spacing is overlapped.


\begin{table}[!h]
\topcaption{Data sets}
\footnotesize \input{tables/c140607_c151022_l001.tex}
\label{tab:datasets_data}
\end{table}
\end{landscape}

\begin{landscape}
\begin{table}[!h]
\topcaption{Simulated background samples}
\tiny \input{tables/c140607_c151022_l002.tex}
\label{tab:datasets_bkg}
\end{table}
\end{landscape}


%%____________________________________________________________________________||
