%%____________________________________________________________________________||
\section{Triggers}
\label{sec:triggers}


\subsection{Hadronic signal region}

In Run 2 the RA1 analysis will aim to retain the low-thresholds of Run 1 with developments to the trigger selection, maintaining sensitivity to signatures of new physics with hadronic energy as low as $\scalht = 200$ GeV. This in part is achieved by a migration to PF-based online jet reconstruction with a reduced radius parameter $\Delta R = 0.4$, which provides improvements in jet energy resolution in high-pileup conditions over calorimeter-based reconstruction and mitigates the effects of pileup contamination within the jet cone.

The hadronic signal selection is performed with $\scalht$-$\alphat$ cross triggers with a second jet threshold requirement (\verb!HLT_PFDijetXXXHTYYYAlphaTZZZ!), which suppresses QCD multijet events whilst maintaining signal acceptance.  A loose calorimeter trigger prefilter is utilised to reduce the pass-through rate prior to track-based reconstruction, ensuring the PF-based filters meet the HLT mean timing limit of $\sim$10 ms. The calorimeter prefilter utilises loose $\scalht$ and dijet $\pt$ requirements in addition to a new variable $\alphat$', defined as $\alphat$ in the limit $\Delta\scalht \rightarrow 0$, which better correlates $\alphat$ between calorimeter and PF-based reconstruction.

Each of the signal triggers uniquely seed a single offline analysis bin with the exception of the highest-$\scalht$ trigger which is utilised for analysis bins above $\scalht > 400$ GeV. Analysis bins at very high-$\scalht$ are seeded by the \verb!HLT_PFHT900! trigger with no explicit dependence on $\alphat$ or second jet threshold. A list of Run 2 triggers for the hadronic signal region in the Run 2 HLT menu are shown in Table~\ref{tab:2015_Hadronic_Signal_Triggers}. The thresholds of the triggers will remain unchanged through run conditions and are measured to give high efficiencies in all three proposed run conditions: PU40bx50, PU20bx25 and PU40bx25. The Level-1 seeds for the HLT paths are given by the disjunction of the lowest unprescaled Level-1 hadronic scalar energy and missing energy sum seeds (\verb!HTTXXX_OR_ETMYYY!) for the run scenario.

Studies are currently underway to extend the trigger strategy to increase acceptance to monojet-like signatures of compressed spectrum and DM models with the transition from a pure dijet $\pt$ requirement to a dijet average $\pt$ trigger, enabling an increase in efficiency in the selection of events exhibiting asymmetric jet topologies.


% TABLE : 2015 triggers
%----------------------------------------------------------------------
\begin{table}[h!]
\topcaption{Hadronic signal region HLT paths for the Run 2 PU40bx25 scenario, lower threshold Level-1 seeds, \texttt{HTT150 OR ETM60}, are utilised for the PU40bx50 and PU20bx50 scenarios. }
\footnotesize
\centering
\begin{tabular}{c|ccc|c} 
\hline
\hline
HLT path & L1 seed & HLT calo-prefilter                      & HLT PF-filter                          & Rate \\[0.7 ex] 
         &         & ($\scalht$, $\alphat$', $\pt^{\rm j2}$) & ($\scalht$, $\alphat$, $\pt^{\rm j2}$) & (Hz) \\[0.7 ex] 
\hline
\verb!HLT_PFDijet90HT200AlphaT0p57! & \verb!HTT175 OR ETM70! & 150, 0.540, 70 & 200, 0.570, 90 & 11.0 $\pm$ 3.0 \\
\verb!HLT_PFDijet90HT250AlphaT0p55! & \verb!HTT175 OR ETM70! & 200, 0.535, 70 & 250, 0.550, 90 & 8.5  $\pm$ 3.0 \\
\verb!HLT_PFDijet90HT300AlphaT0p53! & \verb!HTT175 OR ETM70! & 250, 0.525, 70 & 300, 0.530, 90 & 9.5  $\pm$ 3.0 \\
\verb!HLT_PFDijet90HT350AlphaT0p52! & \verb!HTT175 OR ETM70! & 300, 0.520, 70 & 350, 0.520, 90 & 10.0 $\pm$ 3.0 \\
\verb!HLT_PFDijet90HT400AlphaT0p51! & \verb!HTT175 OR ETM70! & 370, 0.510, 70 & 400, 0.510, 90 & 13.5 $\pm$ 3.5 \\
\hline
\multicolumn{4}{c|}{Exclusive rate (Hz)} & 34 $\pm$ 6 \\
\hline
\hline

\end{tabular}
\label{tab:2015_Hadronic_Signal_Triggers}
\end{table}




%Prescaled control region triggers
\subsection{Control samples}
Prescaled $\scalht$-dijet triggers, each with an exclusive rate of $\sim$1 Hz, are utilised in the selection of events for the hadronic control region. These share the same Level-1 seeds and $\scalht$ threshold of the signal triggers and are similarly each mapped to a unique offline bin. The non-hadronic control regions will be seeded by the lowest-threshold unprescaled triggers of the given run scenario, with \verb!HLT_Ele27_eta2p1_WP75_Gsf! seeding the electron control region ($e$, $ee$), \verb!HLT_IsoMu20_eta2p1! the muon control region ($\mu$, $\mu\mu$) and \verb!HLT_Photon175! the photon control region.





\subsection{Low-$\scalht$ Level-1 seeds}

Some models of new physics, such as supersymmetric compressed spectrum models, are challenging to select at the trigger level due to low-hadronic energy visible in the final state. Sensitivity to such models require low trigger thresholds which is difficult to achieve without incurring a large increase in the Level-1 trigger rate. New Level-1 seeds which enable low thresholds to be utilised by actively vetoing QCD event topologies have been studied and are shown to have higher efficiencies for such models than can be achieved with the current Level-1 menu.

The $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ seed exploits the typical dijet topologies exhibited in QCD dijet production by vetoing events where the azimuthal separation of the leading jets exceeds eight calorimeter regions, corresponding to a veto of: $\Delta\phi(j_{1}^{L1},j_{2}^{L1}) \ge 160^{\circ}$, where a jet threshold of $\pt > 32$ GeV is imposed on the second jet. This enables a much lower threshold on the $\scalht$-leg to be achieved, with a small increase in other thresholds in the menu, enabling for example the rate neutral trigger: \verb!L1_DoubleJetC32_WdPhi7_HTT125! to be utilised.

An alternate $\mht/\scalht$ 'reduced-MHT' seed exploits the correlation in missing hadronic energy and visible hadronic energy typical of decays with genuine $\met$ and the decorrelation of these quantities for QCD with fake-$\met$ by requiring a minimum $\mht/\scalht$ ratio. This again enables triggers with a significant reduction in the threshold on the $\scalht$-leg, for example with the rate neutral trigger: \verb!L1_HTT125_rHTM0p3!.

The logical disjunction of these two seeds can further improve signal efficiency whilst maintaining an effective suppression of QCD events by increasing acceptance to additional topolgies. ISR-dominated final states for instance typically have large $\mht/\scalht$ but may fail the $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ selection, where as events with high jet multiplicities typically have high $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ but may fail the $\mht/\scalht$ threshold due to the breakdown in $\mht/\scalht$ at high jet multiplicities. Combined these seeds allow even smaller thresholds to be used on the $\scalht$-leg without loss of efficiency to ISR-dominated or high jet multiplicity events, for example with the trigger:\\ \verb!L1_HTT110_rHTM0p6_rHTM0p0_WdPhi6!.


\subsubsection{Implementation and performance of low-$\scalht$ Level-1 seeds}

The new trigger seeds can be implemented in the trigger hardware by repurposing the bits currently utilised for $\mht$ and $\phi({\mht})$ trigger primitives with the new $\mht/\scalht$ and $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ primitives respectively. These changes have been discussed with trigger experts and are deemed to be relatively simple to implement in the calorimeter trigger firmware and will have little impact on the operation global trigger. The latest version of the Level-1 trigger emulator currently has the \verb!L1_DoubleJetC32_WdPhi7_HTT125!, \verb!L1_HTT125_rHTM0p3! and \\ \verb!L1_HTT110_rHTM0p6_rHTM0p0_WdPhi6! low-$\scalht$ trigger primitives implemented, enabling a wider study within the collaboration.

The performance after the full offline selection of the low-$\scalht$ Level-1 seeds was studied for a range of signal models in the lowest $\scalht$ and $\njet$ analysis bins which are predominantly populated by compressed models. Performance was measured relative to the current PU40bx25 Level-1 hadronic menu, {\verb!HTT175! \verb!OR! \verb!DoubleJetC100! \verb!OR! \verb!QuadJetC60! \verb!OR! \verb!ETM70!}, with the rate equivalent low-$\scalht$ menues defined as: Low-$\scalht$ seed {\verb!OR! \verb!HTT200! \verb!OR! \verb!DoubleJetC120! \verb!OR! \verb!QuadJetC60! \verb!OR! \verb!ETM70!}. The efficiencies of the proposed menues for $\njet = 2$ and $\njet = 3$, shown in Table~\ref{tab:LowHT_Seed_Signal_2Jet} and Table~\ref{tab:LowHT_Seed_Signal_3Jet} respectively, show significant improvements in trigger efficiency utilising the low-$\scalht$ seeds with respect to the current hadronic menu and similar performance to what could be obtained by reducing the $\met$ threshold without the additional 3 kHz Level-1 trigger rate this would incur.


% TABLE : Low-HT seed efficiencies - NJet = 2
%----------------------------------------------------------------------
\begin{table}[h!]
\topcaption{Trigger efficiency for $\njet = 2$, $200 < \scalht \le 300$ analysis bin and corresponding rate of the current Level-1 hadronic menu and proposed low-$\scalht$ trigger menues for a range of compressed signal models.} %sparticle and LSP masses represented by the first and second bracketed term respectively.}
\footnotesize
\centering
\begin{tabular}{cccccc} 
\hline
\hline
  Signal model & Hadronic menu & $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ & $\mht/\scalht$ &$\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ \verb!OR! $\mht/\scalht$ & Hadronic menu \verb!OR ETM60! \\
\hline
  T2cc(250, 210)   & 0.60 & 0.86 & 0.91 & 0.94 & 0.95 \\
  T2qq(400, 400)   & 0.63 & 0.82 & 0.88 & 0.95 & 0.94 \\
  T2tt(300, 200)   & 0.53 & 0.91 & 0.95 & 0.99 & 0.96 \\
\hline
  Menu rate (kHz) & 15   & 15   & 15   & 15   & 19   \\
\hline
\hline
\end{tabular}
\label{tab:LowHT_Seed_Signal_2Jet}
\end{table}

% TABLE : Low-HT seed efficiencies - NJet = 3
%----------------------------------------------------------------------
\begin{table}[h!]
\topcaption{Trigger efficiency for $\njet = 3$, $200 < \scalht \le 300$ analysis bin and corresponding rate of the current Level-1 hadronic menu and proposed low-$\scalht$ trigger menues for a range of compressed signal models.} %sparticle and LSP masses represented by the first and second bracketed term respectively.}
\footnotesize
\centering
\begin{tabular}{cccccc} 
\hline
\hline
  Signal model & Hadronic menu & $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ & $\mht/\scalht$ &$\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ \verb!OR! $\mht/\scalht$ & Hadronic menu \verb!OR ETM60! \\
\hline
  T2cc(250, 210)   & 0.45 & 0.74 & 0.74 & 0.83 & 0.94 \\
  T2qq(400, 400)   & 0.46 & 0.88 & 0.88 & 0.93 & 0.92 \\
  T2tt(300, 200)   & 0.41 & 0.76 & 0.83 & 0.84 & 0.86 \\
\hline
  Menu rate (kHz) & 15   & 15   & 15   & 15   & 19   \\
\hline
\hline
\end{tabular}
\label{tab:LowHT_Seed_Signal_3Jet}
\end{table}



%%____________________________________________________________________________||
