%%____________________________________________________________________________||
\section{Summary}
\label{sec:summary}

We report on the prospects for a missing energy plus jet search that
is sensitive to models of Supersymmetry and Dark Matter.
The analysis follows an inclusive approach designed to capture a wide
scope of possible final states, use of robust methods to be
insensitive to multijet production, instrumental effects and MC
mis-modelling. Thus making it ideal for early data discoveries.
The Run~1 analysis has been improved in several areas, including an
increase in the acceptance of the signal region and an optimisation of
the signal event categorisation. By relaxing the minimal jet multiplicity 
to a single jet and adding a orthogonal jet selection with a lower 
\Pt requirement on the second leading jet. This leads to 
significantly improved acceptance to compressed SUSY and Dark Matter
models.
%asymetric jet selection. This selection uses an orthogonal requirement
%on the sub-leading jet to improve acceptance for ISR and monojet-type
%final states. This increases the acceptance of an example compressed
%SUSY model by about a factor of three and an example DM model by as
%much as a factor of five.

Candidate signal events are binned according to the number of
reconstructed jets, the number of jets identified to originate from
bottom quarks, and the scalar and vector sums of the transverse energy
of jets. The sum of standard model backgrounds per bin is estimated
from a simultaneous binned likelihood fit to event yields in the
signal region and \mj, \mmj, and \gj control samples. The
%\ej, \eej
analysis relies heavily on methods and cross-checks derived from the
data control samples to demonstrate control of the SM background
predictions. 

%The addition of simplified and heavy quark flavored DM models yields
%to strong results on DM models in the spin-dependent and
%spin-independent nucleon cross section scattering plane in a largely
%model-independent way. These results may provide the strongest
%constraints with early 13~TeV data for low mass Dark Matter and the
%strongest collider constraints across a wide range of masses. In
%particular probe excesses observed in direct detection experiments at
%energies of about 10 GeV but also by the Fermi-LAT (2013) satellite
%indicating a DM particle of about 50 GeV mass. We expect to
%conclusively probe this region with the full Run II dataset.

Preliminary projections are presented for SUSY and DM
simplified models using currently recorded $\sqrt{s} =$ 13~TeV data and
projections assuming $3$\ifb of data.

%The study reveals discovery
%potential for a number of gluino-mediated models with 3\fbinv and
%sensitivity to a broad range of DM models.

%The analysis also has been adapted to latest standards of the CMS
%collaboration. All analysis tools have been ported and verified using
%the \textsc{PHYS14} prescription in {\tt cmgtools}, the use of calojet
%off- and online has been replaced by particle flow (PF) jet and the
%trigger requirements have been adapted to maintain 2012 thresholds.
%Further plans for this analysis will be to improve/increase the
%analysis binning for large $H_\textrm{T}$, improve and maintain
%trigger thresholds using PF trigger paths and evolve the selection
%according to the running conditions with increasing luminosity.

%\begin{itemize}
%  \item summarize the PHYS14 exercise described in the other sections
%  \item mention briefly further preparation plans for Run 2
%  \item conclude with the outlook for Run 2
%\end{itemize}

%%____________________________________________________________________________||
