\clearpage
\section{Low-$\scalht$ Level-1 seeds \label{app:lowHTSeeds}}

Some models of new physics, such as supersymmetric compressed spectrum models, are challenging to select at the trigger level due to low-hadronic energy visible in the final state. Sensitivity to such models require low trigger thresholds which is difficult to achieve without incurring a large increase in the Level-1 trigger rate. New Level-1 seeds which enable low thresholds to be utilised by actively vetoing QCD event topologies have been studied and are shown to have higher efficiencies for such models than can be achieved with the current Level-1 menu.

The $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ seed exploits the typical dijet topologies exhibited in QCD dijet production by vetoing events where the azimuthal separation of the leading jets exceeds eight calorimeter regions, corresponding to a veto of: $\Delta\phi(j_{1}^{L1},j_{2}^{L1}) \ge 160^{\circ}$, where a jet threshold of $\pt > 32$ GeV is imposed on the second jet. This enables a much lower threshold on the $\scalht$-leg to be achieved, with a small increase in other thresholds in the menu, enabling for example the rate neutral trigger: \verb!L1_DoubleJetC32_WdPhi7_HTT125! to be utilised.

An alternate $\mht/\scalht$ 'reduced-MHT' seed exploits the correlation in missing hadronic energy and visible hadronic energy typical of decays with genuine $\met$ and the decorrelation of these quantities for QCD with fake-$\met$ by requiring a minimum $\mht/\scalht$ ratio. This again enables triggers with a significant reduction in the threshold on the $\scalht$-leg, for example with the rate neutral trigger: \verb!L1_HTT125_rHTM0p3!.

The logical disjunction of these two seeds can further improve signal efficiency whilst maintaining an effective suppression of QCD events by increasing acceptance to additional topologies. ISR-dominated final states for instance typically have large $\mht/\scalht$ but may fail the $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ selection, where as events with high jet multiplicities typically have high $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ but may fail the $\mht/\scalht$ threshold due to the breakdown in $\mht/\scalht$ at high jet multiplicities. Combined these seeds allow even smaller thresholds to be used on the $\scalht$-leg without loss of efficiency to ISR-dominated or high jet multiplicity events, for example with the trigger:\\ \verb!L1_HTT110_rHTM0p6_rHTM0p0_WdPhi6!.

The new trigger seeds is implemented in the trigger hardware by repurposing the bits currently utilised for $\mht$ and $\phi({\mht})$ trigger primitives with the new $\mht/\scalht$ and $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ primitives respectively. These changes have been discussed with trigger experts and are deemed to be relatively simple to implement in the calorimeter trigger firmware and has little impact on the operation global trigger. The latest version of the Level-1 trigger emulator currently has the \verb!L1_DoubleJetC32_WdPhi7_HTT125!, \verb!L1_HTT125_rHTM0p3! and \\ \verb!L1_HTT110_rHTM0p6_rHTM0p0_WdPhi6! low-$\scalht$ trigger primitives implemented, enabling a wider study within the collaboration.

The performance after the full offline selection of the low-$\scalht$ Level-1 seeds was studied for a range of signal models in the lowest $\scalht$ and $\njet$ analysis bins which are predominantly populated by compressed models. Performance was measured relative to the current PU40bx25 Level-1 hadronic menu, {\verb!HTT175! \verb!OR! \verb!DoubleJetC100! \verb!OR! \verb!QuadJetC60! \verb!OR! \verb!ETM70!}, with the rate equivalent low-$\scalht$ menues defined as: Low-$\scalht$ seed {\verb!OR! \verb!HTT200! \verb!OR! \verb!DoubleJetC120! \verb!OR! \verb!QuadJetC60! \verb!OR! \verb!ETM70!}. The efficiencies of the proposed menues for $\njet = 2$ and $\njet = 3$, shown in Table~\ref{tab:LowHT_Seed_Signal_2Jet} and Table~\ref{tab:LowHT_Seed_Signal_3Jet} respectively, show significant improvements in trigger efficiency utilising the low-$\scalht$ seeds with respect to the current hadronic menu and similar performance to what could be obtained by reducing the $\met$ threshold without the additional 3 kHz Level-1 trigger rate this would incur.

It is important to note that the new L1 seeds discussed in this
section are currently only potential alternatives to the existing L1
\texttt{ETM} and \texttt{HTT} seeds. Their inclusive may require some
rate balancing within the existing menus at the expense of other
seeds. Studies have considered the re-allocation of rate ($\sim$5~kHz)
from the \texttt{DoubleJetC} seed. The inclusion of these new seeds
may be a beneficial strategy to employ if the thresholds on the
\texttt{ETM} and \texttt{HTT} seeds are to be raised due to increasing
instantaneous luminosity and/or pileup conditions later in the run of
2015.

% TABLE : Low-HT seed efficiencies - NJet = 2
%----------------------------------------------------------------------
\begin{table}[h!]
\topcaption{Trigger efficiency for $\njet = 2$, $200 < \scalht \le 300$ analysis bin and corresponding rate of the current Level-1 hadronic menu and proposed low-$\scalht$ trigger menues for a range of compressed signal models.} %sparticle and LSP masses represented by the first and second bracketed term respectively.}
\footnotesize
\centering
\begin{tabular}{cccccc} 
\hline
\hline
  Signal model & Hadronic menu & $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ & $\mht/\scalht$ &$\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ \verb!OR! $\mht/\scalht$ & Hadronic menu \verb!OR ETM60! \\
\hline
  T2cc(250, 210)   & 0.60 & 0.86 & 0.91 & 0.94 & 0.95 \\
  T2qq(400, 400)   & 0.63 & 0.82 & 0.88 & 0.95 & 0.94 \\
  T2tt(300, 200)   & 0.53 & 0.91 & 0.95 & 0.99 & 0.96 \\
\hline
  Menu rate (kHz) & 15   & 15   & 15   & 15   & 19   \\
\hline
\hline
\end{tabular}
\label{tab:LowHT_Seed_Signal_2Jet}
\end{table}

% TABLE : Low-HT seed efficiencies - NJet = 3
%----------------------------------------------------------------------
\begin{table}[h!]
\topcaption{Trigger efficiency for $\njet = 3$, $200 < \scalht \le 300$ analysis bin and corresponding rate of the current Level-1 hadronic menu and proposed low-$\scalht$ trigger menues for a range of compressed signal models.} %sparticle and LSP masses represented by the first and second bracketed term respectively.}
\footnotesize
\centering
\begin{tabular}{cccccc} 
\hline
\hline
  Signal model & Hadronic menu & $\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ & $\mht/\scalht$ &$\Delta\phi(j_{1}^{L1},j_{2}^{L1})$ \verb!OR! $\mht/\scalht$ & Hadronic menu \verb!OR ETM60! \\
\hline
  T2cc(250, 210)   & 0.45 & 0.74 & 0.74 & 0.83 & 0.94 \\
  T2qq(400, 400)   & 0.46 & 0.88 & 0.88 & 0.93 & 0.92 \\
  T2tt(300, 200)   & 0.41 & 0.76 & 0.83 & 0.84 & 0.86 \\
\hline
  Menu rate (kHz) & 15   & 15   & 15   & 15   & 19   \\
\hline
\hline
\end{tabular}
\label{tab:LowHT_Seed_Signal_3Jet}
\end{table}

