%%__________________________________________________________________||
\section{Background estimation for SM processes with genuine \ETmiss}
\label{sec:ewk_background}

In the absence of multijet events, the background counts in the signal
region arise from SM processes with significant \ETmiss in the final
state. In events with low counts of jets and b-quark jets, the largest
backgrounds with genuine \ETmiss are from the associated production of
W or Z bosons with jets, followed by either the weak decays \znunu or
\wtaunu, where the $\tau$ decays hadronically and is identified as a
jet; or by leptonic decays that are not rejected by the dedicated
electron or muon vetoes. The veto of events containing isolated tracks
is efficient at further suppressing these backgrounds as well as the
single-prong hadronic decay of the tau lepton. At higher jet and
b-quark jet multiplicities, top quark production followed by
semileptonic weak top quark decay becomes important.

The production of W and Z bosons in association with jets, \ttbar and
\gj processes are simulated with the \MADGRAPH V5~\cite{madgraph}
event generator. The production of single-top quark events is
generated with \POWHEG~\cite{powheg}, and diboson events are produced
with \PYTHIA8.1~\cite{pythia8}. For all simulated samples, \PYTHIA8.1
is used to describe parton showering and hadronisation. All samples
are generated using the \textsc{cteq6l1}~\cite{Pumplin:2002vw} parton
distribution functions (PDF). The description of the detector response
is implemented using the \GEANTfour~\cite{geant} package. The
simulated samples are normalised using the most accurate cross section
calculations currently available, usually with
next-to-next-to-leading-order (NNLO) accuracy. To model the effects of
pileup, the simulated events are generated with a nominal distribution
of pp interactions per bunch crossing and then reweighted to match the
pileup distribution as measured in data.

The method to estimate the non-multijet backgrounds in the signal
region relies on the use of transfer factors, which are constructed
per bin (in terms of \njet, \nb, and \scalht) per data control
sample. The transfer factors are determined from the simulated event
samples and are ratios of expected yields in the corresponding bins of
the signal region and control samples. The transfer factors are used
to extrapolate from the event yields measured in a data control
samples to an expectation for the total background event yields in the
signal region.

Three disjoint data control regions, binned identically to the signal
region, are used to estimate the contributions from the various
remaining SM background processes. The control regions are defined by
a selection of \mj, \mmj, and \gj events. The selection criteria are
chosen such that the SM processes and their kinematic properties
resemble as closely as possible the SM background behaviour in the
signal region once the muon, dimuon system, or photon are ignored when
computing quantities such as \scalht, \mht and \alphat. The baseline
selection criteria and binning definition described in
Table~\ref{tab:selections} are applied to all control samples, except
for the lepton and photon vetoes, which are inverted and tightened to
improve purity. The event selection criteria are defined to also
ensure that any potential contamination from multijet events or a wide
variety of SUSY models (\ie signal contamination) is negligible.

The \mj sample is recorded using a trigger condition that requires an
isolated muon and the event selection criteria are chosen in order to
ensure high trigger efficiency. Furthermore, the muon is required to
be well separated from the jets in the event and the transverse mass
($M_{\rm T}$) of the muon and \ETmiss~\cite{CMS-PAS-PFT-09-001,
  CMS-PAS-PFT-10-001} system must satisfy $30 < M_{\rm T} < 125\gev$
to ensure a sample rich in W bosons (produced promptly or from the
decay of top quarks). The \mmj sample uses similar selection criteria
as the \mj sample and the same trigger condition. Exactly two
oppositely-charged, isolated muons are required, the muons must be
distanced from the jets in the event, and the invariant mass of the
dimuon system must be within a window of $\pm 25\GeV$ around the mass
of the Z boson. For both the muon and dimuon samples, no requirement
is made on the variable \alphat in order to increase the statistical
precision of the predictions derived from these samples.  The \gj
sample is recorded using a single photon trigger condition. The event
selection criteria comprise an isolated photon with $\Et > 200\gev$
and $\scalht > 400\GeV$.

Three independent estimates of the irreducible background of \znunu +
jets events are determined from the \gj, \mmj, amd \mj data control
samples. The \gj and \zmumu + jets processes have similar kinematic
properties when the photon or muons are ignored~\cite{Bern:2011pa}
albeit different acceptances. In addition, the \gj process has a
larger production cross section than \znunu + jets events. The \mj
data sample is used to provide an estimate for the \znunu\ + jets
contribution as well as the other dominant SM processes, \ttbar and W
boson production. Residual contributions from processes such as
single-top-quark, diboson, and Drell-Yan production are also included.

\begin{table}[thp!]
  \caption{%CMS {\it Preliminary}, $\mathcal{L}_{\mathrm{int}} =
    % 2.2\fbinv$, $\sqrt{s} = 13\TeV$. 
    % \newline
    Systematic uncertainties (percent) in the estimates of the
    normalisation of the SM background components as a function of
    \njet, as determined from ensembles of closure tests based on
    multiple data control samples. The quoted ranges correspond to the 
    variations determined across the \nb and \scalht bins of a given \njet
    category. The additional contributions listed at the foot of the
    table are added in quadrature to the \njet-dependent contributions
    for each SM background component. } 
  \label{tab:bkgd_systs}
  \centering
  \footnotesize
  \begin{tabular}{ lcc }
    \hline
    \hline
    \njet                         & \multicolumn{2}{c}{Uncertainty (\%) in background component} \\
    \cline{2-3}
                                  & \ttbar, W+jets, residual SM & \znunu\ + jets                 \\
    \hline
    \multicolumn{2}{l}{``Monojet'':}                                                             \\
    1                             & 9--36                       & 9--36                          \\
    \hline
    \multicolumn{2}{l}{``Asymmetric'':}                                                          \\
    2                             & 11--105                     & 9--46                          \\
    3                             & 12--86                      & 12--78                         \\
    4                             & 16--52                      & 13--43                         \\
    $\geq$5                       & 19--47                      & 27--73                         \\
    \hline
    \multicolumn{2}{l}{``Symmetric'':}                                                           \\
    2                             & 7--34                       & 11--30                         \\
    3                             & 9--31                       & 13--44                         \\
    4                             & 13--36                      & 8--34                          \\
    $\geq$5                       & 15--22                      & 17--28                         \\
    \hline
    \multicolumn{2}{l}{Additional contributions:}                                                \\
    \alphat ($\scalht < 800\gev$) & 10-27                       & 10-27                          \\
    \dphi ($\scalht > 800\gev$)   & 22                          & 22                             \\
    b-quark identification        & $<$5                        & $<$5                           \\
    \hline
    \hline
  \end{tabular}
\end{table}

The uncertainty in the transfer factors derived from simulation is
probed through closure tests based on data control
samples~\cite{RA1Paper2012}. Each closure test inspects the
compatibility of yields in two disjoint data control samples and a
corresponding transfer factor derived from simulation. A large
ensemble of tests are performed to probe the simulation modelling of a
range of key physics effects that may lead to potential biases in the
transfer factors~\cite{RA1Paper2012}. For the analysed data sample,
the closure tests reveal no significant biases or dependencies on
\njet or \scalht for all individual tests. Systematic uncertainties in
the transfer factors are typically determined from ensembles of
closure tests, which can be considered as ``normalisation''
uncertainties for a given component of background events categorised
according to \njet, \nb, and \scalht.  Table~\ref{tab:bkgd_systs}
summarises typical values for the systematic uncertainties in
experimental acceptance effects for the dominant SM background
components. These uncertainties are assumed to be fully uncorrelated
for events catogorised differently in \njet, \nb, and \scalht. The
uncertainties associated with extrapolations in the \alphat and \dphi
variables, and the simulation modelling of the efficiency and mistag
rates for identifying jets originating from b quarks or light-flavour
partons are also listed, which are assumed to be fully correlated
across the \nb dimension only.

Templates derived from simulation are used to predict the background
counts in the \mht dimension. Multiple data control regions are used
to evaluate the degree to which the simulation describes the \mht
distributions observed in data and to assign appropriate systematic
uncertainties, which can be in excess of $>100\%$ in the most
sensitive \mht bins.

%%__________________________________________________________________||
