%%__________________________________________________________________||
\subsection{Backgrounds with genuine \texorpdfstring{\ETmiss}{MET}}
\label{sec:ewk_background}

Following the suppression of multijet events through the use of the
\alphat and \bdphi variables, the dominant nonmultijet backgrounds
involve SM processes that produce high-\Pt neutrinos in the final
state. In events with few jets or few b quark jets, the associated
production of W or Z bosons and jets, with the decays $\PW^\pm
\!\rightarrow\! \ell\nu$ ($\ell=\Pe$, $\Pgm$, $\Pgt$) or \znunu,
dominate the background counts. For W boson decays that yield a muon
or electron (possibly originating from leptonic $\Pgt$ decays), the
background arises when the event containing the $\Pgm$ or $\Pe$ is not
rejected by the lepton vetoes. Background also arises when the $\tau$
lepton decays to hadrons, identified as a jet, and neutrinos. The veto
of events containing at least one isolated track is efficient at
further suppressing these backgrounds, including those from
single-prong $\tau$-lepton decays. At higher jet or b quark jet
multiplicities, single top and \ttbar production, followed by
semileptonic top quark decay, also become an important source of
background.

The method to estimate the nonmultijet backgrounds in the signal
region relies on the use of transfer factors determined from
simulation that are constructed per bin (in terms of \njet, \nb, and
\scalht) per control region. Each transfer factor is defined as the
ratio of the expected yields in the same (\njet, \nb, \scalht) bins of
the signal region $\mathcal{N}^\text{SR}_\text{MC}$ and one of the
control regions $\mathcal{N}^\text{CR}_\text{MC}$. The transfer
factors are used to extrapolate from the event yields observed in each
bin of a data control sample $\mathcal{N}^\text{CR}_\text{data}$ to
provide an estimate for the background, intergrated over \HTmiss, from
a particular SM process or processes in the corresponding bin of the
signal region $\mathcal{N}^\text{SR}_\text{data}$. The superscript SR
or CR refers to, respectively, the process or processes being
estimated and one of the \mj, \mmj, and \gj control regions, described
in Section~\ref{sec:control_regions}. The subscript refers to whether
the counts are obtained from data, simulation (``MC'') or an estimate
(``pred'').

The method aims to minimise the effects of simulation mismodelling, as
many systematic biases in the simulation are expected to largely
cancel in the transfer factors, given that the events in any given
(\njet, \nb, \scalht) bin of the control regions closely mirror those
in the corresponding bin in the signal region, in terms of the event
scale and topology, the kinematical phase, and the relative background
compositions. In short, minimal extrapolations are made. Uncertainties
in the transfers factors are determined from a data-derived approach,
described below.

Three independent estimates of the irreducible background of \znunu +
jets events are determined from the \gj, \mmj, amd \mj data control
samples. The \gj and \zmumu + jets processes have similar kinematic
properties when the photon or muons are ignored~\cite{Bern:2011pa},
albeit different acceptances. In addition, the \gj process has a
larger production cross section than \znunu + jets events. The \mj
data sample is used to provide an estimate for both the \znunu\ + jets
background, as well as the other dominant SM processes, \ttbar and W
boson production (labelled collectively as $\PW/\ttbar$). Residual
contributions from all other SM relevant processes, such as
single-top-quark, diboson, and Drell-Yan production, are also included
as part of the $\PW/\ttbar$ estimate from the \mj sample. The
definition of the various transfer factors used in the search are
given below:

\begin{eqnarray} 
  \mathcal{N}^\text{\PW/\ttbar}_\text{pred} & = & 
  \bigg( 
  \frac{\,\mathcal{N}^\text{\PW/\ttbar}_\text{MC}\,}
  {\mathcal{N}^\text{\mj}_\text{MC}}
  \bigg)\,
  \mathcal{N}^\text{\mj}_\text{data} \\
  \mathcal{N}^\text{\znunu}_\text{pred} & = & 
  \bigg( 
  \frac{\,\mathcal{N}^\text{\znunu}_\text{MC}\,}
  {\mathcal{N}^\text{\mj}_\text{MC}}
  \bigg)\,
  \mathcal{N}^\text{\mj}_\text{data} \\
  \mathcal{N}^\text{\znunu}_\text{pred} & = & 
  \bigg( 
  \frac{\,\mathcal{N}^\text{\znunu}_\text{MC}\,}
  {\mathcal{N}^\text{\mmj}_\text{MC}}
  \bigg)\,
  \mathcal{N}^\text{\mmj}_\text{data} \\
  \mathcal{N}^\text{\znunu}_\text{pred} & = & 
  \bigg( 
  \frac{\,\mathcal{N}^\text{\znunu}_\text{MC}\,}
  {\mathcal{N}^\text{\gj}_\text{MC}}
  \bigg)\,
  \mathcal{N}^\text{\gj}_\text{data} 
\end{eqnarray} 

The likelihood function, described in Section~\ref{sec:result},
encodes the estimate via the transfer factors of the $\PW/\ttbar$
background, as well as the three independent estimates of the \znunu
background, which are considered simultaneously.

\newcommand{\phh}{\ensuremath{\phantom{1-}}}
\begin{table*}[h!]
  \caption{
    Systematic uncertainties (percent) in the transfer factors used in
    the method to estimate the SM backgrounds with genuine \ptvecmiss
    in the signal region. The quoted ranges provide representative
    values of the observed variations as a function of \njet and
    \scalht. 
  } 
  \label{tab:bkgd_systs}
  \centering
  \footnotesize
  \begin{tabular}{ lrrrr }
    \hline
    Systematic           & \multicolumn{4}{c}{Uncertainty in transfer factor [\%]} \\
    \cline{2-5} 
    source               & $\mj \Rightarrow \ttbar/\PW$ 
                         & $\mj \Rightarrow \znunu$ 
                         & $\mmj \Rightarrow \znunu$ 
                         & $\gj \Rightarrow \znunu$                                \\
    \hline                                                    
    \multicolumn{5}{l}{\it Scale factors (applied to simulation):}                 \\
    Jet energy scale     & $<15\%$    & $<15\%$   & $<10\%$   & $<15\%$            \\
    b-tag eff. \ mistag  & $<5\%$     & $<5\%$    & $<2\%$    & $<2\%$             \\
    Lepton SFs           & $2-5\%$    & $2-5\%$   & $2-5\%$   & $-$                \\
    Pileup               & $<10\%$    & $<6\%$    & $<4\%$    & $<3\%$             \\
    Top quark \Pt        & $<5\%$     & $<20\%$   & $<4\%$    & $-$                \\ [0.5ex]
    \multicolumn{5}{l}{\it Closure tests:}                                         \\
    W/Z ratio            & $-$        & $10-30\%$ & $-$       & $-$                \\
    Z/$\gamma$ ratio     & $-$        & $-$       & $-$       & $10-30\%$          \\
    W/\ttbar composition & $10-100\%$ & $-$       & $-$       & $-$                \\
    W polarisation       & $5-50\%$   & $5-50\%$  & $-$       & $-$                \\
    $\alphat\,/\,\bdphi$ & $5-80\%$   & $5-80\%$  & $50-80\%$ & $-$                \\
    \hline
  \end{tabular}
\end{table*}

Several sources of uncertainty in the transfer factors are evaluated.
The most relevant effects are discussed below, and generally fall into
one of two categories. The first category concerns uncertainties in
``scale factor'' corrections applied to simulation, which are
determined using inclusive data samples that are defined by loose
selection criteria, to account for the mismodelling of theoretical and
experimental parameters. The second category concerns ``closure
tests'' in data that probe various aspects of the accuracy of the
simulation to model correctly the transfer factors in the phase space
of this search.

The uncertainties in the transfer factors are studied for variations
in scale factors related to: the jet energy scale (that result in
changes as large as $\sim$15\%), the efficiency and misidentification
probability of b quark jets (up to 5\%), and the efficiency to
identify well-reconstructed, isolated leptons (up to $\sim$5\%). A 5\%
uncertainty in the minimum bias cross section, $\sigma_\text{MB} =
69.0 \pm 3.5\unit{mb}$, is assumed and propagated through to the
reweighting procedure to account for differences between the simulated
and data-derived measurements of the pileup distributions, which
results in changes of up to $\sim$10\%. The modelling of the
transverse momentum of top quarks ($\Pt^\text{t}$) is evaluated by
comparing the simulated and measured \Pt spectra of reconstructed top
objects in \ttbar events, using the technique described in
Ref.~\cite{}. Simulated events are reweighted according to scale
factors that decrease from a value of $\sim$1.2 to $\sim$0.7, with
uncertainties of $\sim$0.1, within the range $0 < \Pt^\text{t} <
400\GeV$. The resulting change in the transfer factors is as large as
$\sim$20\%. These uncertainties, resulting from variations in scale
factors, are summarised in Table~\ref{tab:bkgd_systs}, along with
representative magnitudes. Each source of uncertainty is assumed to
vary with a fully correlated behaviour across the full phase space of
the signal and control regions.

The second category of sources of uncertainty are determined from sets
of ``closure tests'' based on data control
samples~\cite{RA1Paper2012}. Each set uses the observed event counts
in up to eight bins in \scalht for each of the nine \njet event
categories in one of the three independent data control regions, along
with the corresponding transfer factors determined from simulation, to
obtain a prediction, $\mathcal{N}^\text{pred}(\njet, \scalht)$, of the
observed yields, $\mathcal{N}^\text{obs}(\njet, \scalht)$, in another
control sample (or, in one case, \nb event category).

Each set of tests is designed to target a specific (potential) source
of bias in the simulation modelling that may introduce an \njet- or
\scalht-dependent source of systematic bias in the transfer
factors~\cite{RA1Paper2012}. Several sets of tests are performed. The
$\PZ/\gamma$ ratio determined from simulation is tested against the
same ratio measured using \zmumuj events and the \gj sample. The
$\PW/\PZ$ ratio is also probed using the \mj and \mmj samples. A
further set probes the modelling of the relative composition between
\wlj and \ttbar events using \mj events containing exactly zero or
one more b-tagged jets, which represents a larger extrapolation in
relative composition than used in the search.  The effects of W
polarisation are probed by using \mj events with a positively charged
muon to predict those containing a negatively charged muon. Finally,
the accuracy of the modelling of the efficiencies of the \alphat and
\bdphi requirements are estimated using the \mj sample.

For each set of tests, the level of closure, %$\mathcal{C} =
($\mathcal{N}^\text{obs} - \mathcal{N}^\text{pred}) /
\mathcal{N}^\text{obs}$, which considers only statistical
uncertainties, is inspected to ensure no statistically significant
biases are observed as a function of the nine \njet categories or the
eight \scalht bins. In the absence of such a bias, the level of
closure is recomputed by integrating over either all monojet and
asymmetric \njet categories, or the symmetric \njet categories. The
level of closure and its statistical uncertainty are combined in
quadrature to determine additional contributions to the uncertainties
in the transfer factors. These uncertainties are considered to be
fully correlated between the monojet and asymmetric \njet categories
or the symmetric \njet categories, and fully uncorrelated between
these two regions in \njet and \scalht bins. If the closure tests use
the \mmj sample, the level of closure is determined by additionally
integrating over pairs of adjacent \scalht bins. These uncertainties,
derived from the closure tests in data, are summarised in
Table~\ref{tab:bkgd_systs}, along with representative
magnitudes. These uncertainties are the dominant contribution to the
total, due to the limited number of events in the data control
regions.

%%%%%

% and to
%assign appropriate systematic uncertainties that can be in excess of
%$>100\%$ in the most sensitive \HTmiss bins. Independent systematic
%uncertainties in the templates for the \znunu + jets background and
%the W + jets and \ttbar backgrounds are treated as fully uncorrelated
%across \njet and \nb categories and \scalht bins, and with respect to
%the ``normalisation'' systematic uncertainties summarised in
%Table~\ref{tab:bkgd_systs}.

%%%%%

As introduced in Section~\ref{sec:mht_templates}, templates are
derived from simulation to predict the background counts in the
\HTmiss dimension. The uncertainties in the transfer factors are used
to constrain the normalisation of the \HTmiss templates. The
uncertainties in the \HTmiss shape are discussed below.

%The highly granular binning in \njet and \scalht ensures that events
%categorised by \njet and within the same \scalht bin are produced at a
%similar scale. The effects of missing higher-order calculations in the
%simulated samples are largely mitigated through the transfer factor
%approach and the reliance of measurements in data from multiple
%control regions. Hence, the scale, which is manifest in the
%normalisation of the expected counts integrated over \HTmiss, is
%controlled accurately via the use of transfer factors and measurements
%in data control regions. As a consequence, the simulation is expected
%to accurately model the \HTmiss distribution in data. This assumption is
%based on the expectation that the simulation is able to accurately
%describe the kinematics of events at a similar scale. Conversely, an
%accurate kinematical description is not expected if events of
%different scales are allowed to mix.

The accuracy to which the simulation describes the \HTmiss distributions
is evaluated with respect to data, in each (\njet,\nb, \scalht) bin in
each of the \mj, \mmj, and \gj data control regions. %
The level of agreement between data and simulation as a function of
\HTmiss is parameterised using an orthogonal first-order polynomial,
$f(x) = p_0 + p_1(\bar{x}-x)$, and described by two uncorrelated
parameters, $p_0$ and $p_1$. A binned likelihood fit is performed in
each (\njet, \nb, \scalht) bin of each control region, and the best
fit value $p_1$ and its uncertainty is used to determine the presence
of biases dependent on \HTmiss. The pull of $p_1$ from a value of zero
is defined as the best fit value over its standard deviation,
considering only statistical uncertainties associated with the finite
size of the data and simulated samples.

The lower bound of the final (open) bin in \HTmiss is not more than
800\GeV and is bounded from above by the upper bound of the \scalht
bin in question. The lower bound of the final \HTmiss bin is merged
with lower bins if fewer than ten events in the data control regions
are observed. If a bin in (\njet,\nb, \scalht) contains fewer than ten
events, the \HTmiss template is not used. The merging of bins is
typically only relevant for event categories that satisfy $\nb \geq
2$.

The presence or otherwise of systematic biases is evaluated at a
statistical level, by considering the distribution of pulls obtained
from each control region, which are consistent with statistical
fluctuations, with no indication of trends across the full phase space
of each control region. The $p$-values obtained from the fits are
uniformly distributed. 

The uncertainty in the \HTmiss modelling is extracted under the
hypothesis of no bias. This is done using the maximum likelihood (ML)
values of the fit parameters to determine the statistical precision to
which this hypothesis can be confirmed. The quadrature sum of the ML
value and its uncertainty for $p_1$ from each fit is used to define
alternative templates that represent $\pm1\sigma$ variations to the
nominal \HTmiss template. These alternative templates are encoded in
the likelihood function, as described in Section~\ref{sec:result}. The
observed variations are compatible with the expected values obtained
from studies relying only on simulated event samples. The
uncertainties in the final \HTmiss bin of the templates depend on the
event category and \scalht bin, but are typically found to be in the
range $\sim$10--100\%.

The effect on the \HTmiss templates is determined under $\pm1\sigma$
variations in the jet energy scale, the efficiency and
misidentification probability of b quark jets, the efficiency to
identify well-reconstructed, isolated leptons, the pileup reweighting,
and the modelling in the top quark transverse momentum. These effects
are easily covered by the data-derived uncertainties, described above,
across the full phase space of the control regions, which mirror
closely that of the signal region.




% A check has also been performed on the systematic effect on the
% background prediction due to QCD contamination in the control
% samples, which has been found to be at the 5\% level for the gamma +
% jets control region. Applying an arbitrarily large variation of
% +/-100\% on the number of Monte Carlo QCD events leads to a
% systematic variation on the transfer factors of at most 5%
% in the majority of bins. This preliminary study suggests that effect
% from QCD contamination in the gamma + jets control region is small
% compared to the total uncertainty assigned to transfer factors. This
% systematic source is covered anyway in the data-driven study using
% the photon control region, described in Sec. 12.2.

%The choice of PDF set, or variations therein, predominantly affects
%$\mathcal{A}\times\varepsilon$ through changes in the \Pt spectrum of
%the system recoil. Uncertainties in $\mathcal{A}\times\varepsilon$ due
%to variations in the renormalisation and factorisation scales are
%determined to be relatively small. In both cases, contributions to the
%uncertainty in the theory production cross section are considered.

%Uncertainties in the acceptance associated with the PDFs,
%including those related to the renormalization and factorization
%scales, are evaluated by varying the PDF sets used to produce the
%simulated samples. These uncertainties are defined by the maximum
%deviations observed from 100 variations of the NNPDF3.0LO PDFs for tt
%and W+jets events. 
